---
title: "Homework 02"
author: "Ming Lin"
output: pdf_document
output_file: "./MA331/hw02/homework02.pdf"
---

I pledge my honor that I have abided by the Stevens Honor System 
  
```{r echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
p <- 0.4
n <- c(20, 30, 50, 75, 100)

for (i in 1:length(n)) {
  F[i] = pbinom(8.25, n[i], p)
}


```
Problem 1(i)  
  
For, n = 20, P(N <= 8.5) = `r F[1]`  
For, n = 30, P(N <= 8.5) = `r F[2]`  
For, n = 50, P(N <= 8.5) = `r F[3]`  
For, n = 75, P(N <= 8.5) = `r F[4]`  
For, n = 100, P(N <= 8.5) = `r F[5]` 

Problem 1(ii)  

For, n = 20, P(N <= 8.5) = 0.6331  
For, n = 30, P(N <= 8.5) = 0.0606      
For, n = 50, P(N <= 8.5) = 0.00058  
For, n = 75, P(N <= 8.5) = 1.475e^-7     
For, n = 100, P(N <= 8.5) = 8.91e^-11   

Problem 1(iii)  

```{r echo=FALSE, out.width="50%", out.height= "50%", fig.align='left'}
y <- c(0.0375013,0.03341122,0.0003494771,-0.00060031418,0.00013653601)
plot(n,y)
```  

Problem 1(iv)  
As the errors downtrend to nearly but not 0, the N increases.  

Problem 2  

```{r echo=FALSE}
func <- function(n) {
  x <- vector(mode = "numeric")
  y <- vector(mode = "numeric")
  for (i in 1:100) {
    val <- rnorm(n, mean = 2, sd = 3)
    meanx <- mean(val)
    varx <- sd(val)^2
    x[i] <- meanx - 2 / sqrt(9 / n)
    y[i] <- ((n - 1) * varx) / (9)
  }
  plot(x, y, main="Scatter Plot")
  plot(density(x), main = "Density[Y]")
  plot(density(y), main = "Density[X]")
}
```

```{r, out.width="30%"}
print('N = 20')
func(20)
print("N = 30")
func(30)
print("N = 50")
func(50)
print("N = 75")
func(75)
```

Problem 2(v)  

After observing the plots, I notice that the values seem to peak
in the middle and through sample size n that throughout each
graph their slope and pattern are similar

Problem 2(vi)  

After observing the scatter plots, I noticed that the values are uniformly
randomly distributed in the middle of the scatter plot. Also, the scatter plot
shows minimal correlation and increasing density in the middle.

Problem 3  

![](/Users/minglin/Stevens-IT/MA331/hw02/prob3.pdf)

Problem 4  

![](/Users/minglin/Stevens-IT/MA331/hw02/prob4.pdf)

